---
title: "Addressing Research Challenges"
author: "Dany Mukesha"
date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('CiteAnalyzer')`"
output: 
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Addressing Research Challenges}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

CiteAnalyzer specifically addresses several challenges that researchers face:

### 1. **Google Scholar Blocking Prevention**

The package includes built-in rate limiting and retry mechanisms to prevent 
Google Scholar from blocking requests:

```{r addressing_research_challenges}
# The ExtractScholarData function automatically handles:
# - Rate limiting between requests
# - Retry attempts on failures
# - User agent rotation
# - Request timeouts
```

### 2. **Data Reproducibility**

All analysis functions return structured S4 objects that can be saved and
shared:

```{r data_reproducibility, eval=FALSE}
# Save scholar data for reproducibility
saveRDS(scholar_data, "scholar_analysis.rds")

# Load later for consistent results
loaded_data <- readRDS("scholar_analysis.rds")
```

### 3. **Comprehensive Metric Calculation**

Beyond standard metrics, CiteAnalyzer provides:
- m-index (normalized h-index by career years)
- Citation per paper ratios
- Field-weighted citation impact estimates
- Journal impact factor estimation

### 4. **Integration with Bioconductor Workflows**

The package uses Bioconductor S4 classes and integrates with other 
Bioconductor packages:

```{r bioc_wf_integration}
# Works with BiocParallel for large-scale analysis
# library(BiocParallel)
# results <- bplapply(scholar_ids, function(id) {
#     ExtractScholarData(id, max_publications = 20)
# })
```

## Session Information

```{r eval=FALSE}
sessionInfo()
```
