---
title: "CiteAnalyzer"
subtitle: "Citation Analysis from Google Scholar"
author: "Dany Mukesha"
abstract: "Existing tools for Google Scholar citation analysis face
    significant limitations including frequent blocking due to aggressive 
    scraping, lack of reproducible workflows, and limited analytical 
    capabilities beyond basic metrics. CiteAnalyzer addresses these 
    challenges through a Bioconductor-compliant R package that implements 
    ethical data extraction protocols with adaptive rate limiting, 
    automatic retry mechanisms, and user-agent rotation to prevent service 
    disruption. The package introduces a robust S4 class system for 
    structured data storage and reproducible analysis workflows, enabling 
    calculation of both standard metrics (h-index, i10-index, m-index) and 
    advanced field-weighted impact scores. CiteAnalyzer uniquely integrates 
    collaboration network analysis through co-citation network generation 
    and community detection algorithms, providing insights into research 
    communities and potential collaboration opportunities. 
    
    The tool includes publication-quality visualization tools for temporal
    trend analysis, multi-scholar comparison, and interactive network 
    exploration. Designed specifically for bioinformatics researchers and 
    bibliometric analysts, CiteAnalyzer follows Bioconductor standards for 
    documentation, testing, and parallel processing integration. 
    
    CiteAnalyzer empowers researchers to conduct ethical, reproducible, and 
    sophisticated citation analysis that reveals deeper insights into 
    scientific impact and collaboration patterns than previously possible 
    with existing tools."
date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('CiteAnalyzer')`"
output: 
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{CiteAnalyzer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 6,
  warning = FALSE,
  message = FALSE
)
```

## Introduction

**CiteAnalyzer** is designed for citation analysis from Google Scholar data. 
It addresses key common challenges face when analyzing citation data, 
including:

- **Rate limiting and blocking prevention** through built-in request 
throttling
- **Comprehensive metrics calculation** beyond basic h-index and i10-index
- **Multi-scholar comparison** with normalized ranking systems
- **Collaboration network analysis** to identify research communities
- **Temporal trend analysis** to track research impact over time
- **Publication impact visualization** with interactive plots

Unlike existing tools, CiteAnalyzer ensures reproducibility, robust error
handling, and integration with biological research workflows.

## Installation

To install CiteAnalyzer from Bioconductor:

```{r include=FALSE, eval=FALSE}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("CiteAnalyzer")
```

Or install the development version from GitHub:

```{r installation, eval=FALSE}
remotes::install_github("danymukesha/CiteAnalyzer")
```

## Basic Usage

### Creating a Scholar Profile

The primary function for extracting Google Scholar data is 
`ExtractScholarData()`. This function includes built-in rate limiting 
to prevent Google Scholar from blocking requests.

```{r extract}
library(CiteAnalyzer)

# Extract data for a scholar (replace with actual Google Scholar ID)
# For demonstration, we'll use a sample ID
scholar_data <- ExtractScholarData("qc6CJjYAAAAJ", max_publications = 50,
                                   cache_dir = "temp/")

# View basic information
print(scholar_data@name)
print(scholar_data@affiliation)
print(scholar_data@interests)
```

### Calculating Metrics

CiteAnalyzer provides metric calculation beyond standard indices:

```{r calculate_metrics}
# Calculate all available metrics
metrics <- GetScholarMetrics(scholar_data)

# View results
print(metrics)

# Calculate specific metrics
h_index <- calculate_h_index(scholar_data@publications$citedby)
i10_index <- calculate_i10_index(scholar_data@publications$citedby)
m_index <- calculate_m_index(
    h_index, 
    min(scholar_data@publications$year, na.rm = TRUE)
)

cat(sprintf("h-index: %d\ni10-index: %d\nm-index: %.2f\n",
            h_index, i10_index, m_index))
```

### Visualizing Citation Impact

The package provides several visualization functions to help interpret 
citation data:

```{r visualize_metrics}
# Plot top publications by citations
p1 <- PlotCitationImpact(scholar_data, plot_type = "summary")
print(p1)

# Plot publication and citation timeline
p2 <- PlotCitationImpact(scholar_data, plot_type = "timeline")
print(p2)
```

## Advanced Analysis

### Comparing Multiple Scholars

CiteAnalyzer excels at comparing multiple scholars using normalized metrics:

```{r comparing_multiple_scholars}
# Extract data for multiple scholars
scholar1 <- ExtractScholarData("qc6CJjYAAAAJ", max_publications = 30, 
                               cache_dir = "temp")
scholar2 <- ExtractScholarData("VWCHlwkAAAAJ", max_publications = 30,
                               cache_dir = "temp")
scholar3 <- ExtractScholarData("vzXv764AAAAJ", max_publications = 30,
                               cache_dir = "temp")

# Compare scholars
comparison <- CompareScholars(list(scholar1, scholar2, scholar3))

# View comparison results
print(comparison)

# Create comparison visualization
p3 <- PlotCitationImpact(scholar1, plot_type = "comparison", 
                        compare_with = list(scholar2, scholar3), 
                        radar_coord = "polar")
print(p3)
```

### Analyzing Citation Trends

Track how citation patterns evolve over time:

```{r analyze_citation_trends}
# Analyze trends for multiple scholars
trends <- AnalyzeCitationTrends(list(scholar1, scholar2, scholar3), time_period = "10y")

# Plot publication trends
p4 <- PlotPublicationTrends(list(scholar1, scholar2, scholar3), trend_type = "both")
print(p4)
```

### Finding Collaborators

Identify potential research collaborators based on similarity metrics:

```{r finding_collabos}
# Find potential collaborators for scholar1
collaborators <- FindCollaborators(scholar1, list(scholar2, scholar3), min_similarity = 0.2)

# View results
print(collaborators)
```

### Network Analysis

Visualize collaboration networks between researchers:

```{r network_analysis}
# Create citation network
network <- CreateCitationNetwork(list(scholar1, scholar2, scholar3), min_citations = 5)

# Plot collaboration network
if (igraph::gsize(network) > 0) {
    p5 <- PlotCollaborationNetwork(network, layout_type = "fr")
    print(p5)
}
```


## Conclusion

CiteAnalyzer provides a toolkit for citation analysis from Google Scholar 
data. By addressing key challenges like rate limiting, reproducibility, and
metric calculation, it enables the user to gain deeper insights into research
impact and collaboration patterns.

The implement structured S4 classes, extensive documentation, and 
visualization capabilities make it suitable for both individual users and
large-scale bibliometric studies. 

Future versions will include integration with additional citation databases
and more sophisticated network analysis algorithms.

## Session Information

```{r}
sessionInfo()
```
